### 2023-06-19 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Formulation}Formulation}
\todo[inline]{Changes to be made to Figure~\ref{fig:schematic}.}
\begin{itemize}
  \item Remove labels $\Gamma$, $\Omega$, $\gamma$
  \item Line on vesicle is too thick and change color scheme to same as
    Fig 2
  \item Change to a confined geometry that we use (stenosis)
  \item Show a couple of vesicle shapes and the parabolic profile at
    the inlet, outlet, and in the middle
\end{itemize}

We consider a single multicomponent vesicle $\omega$ with boundary $\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with boundary $\Gamma$ (Figure~\ref{fig:schematic}).
\begin{figure}[H]
  \centering
  \includegraphics[trim = 0.3cm 0cm 1cm 0cm, clip=true,width=0.9\columnwidth]{figures/schematic.pdf}
  \caption{\label{fig:schematic}\small A single multicomponent vesicle
  with boundary $\gamma$ suspended in a domain $\Omega$ with boundary
  $\Gamma$. The dark red regions are the ``stiff'' regions corresponding
  to the maximum bending stiffness $b_{\max}=1$. The dark blue regions
  are the ``floppy'' regions corresponding to the minimum bending
  stiffness $b_{\min}=0.1$ The vesicle dynamics are determined by a
  combination of phase, bending, and tension energies, and an imposed
  flow on $\Gamma$. }
\end{figure}
The fluid is assumed to have zero Reynolds number and is therefore governed by the incompressible Stokes equations
\begin{align}
    \nabla \cdot \TT = 0 \quad \text{and} \quad \nabla \cdot \uu = 0, 
        \quad \xx \in \Omega \backslash \gamma,
\end{align}
where $\TT = -p\mathbf{I} + \mu\left(\nabla \uu + \nabla \uu^T \right)$
is the hydrodynamic stress tensor, $\uu$ is the velocity, $p$ is the
pressure, and $\mu$ is the fluid viscosity. Across the vesicle membrane,
we require that the velocity is continuous and locally inextensible, and
the membrane and hydrodynamic forces balance
\begin{align}
  \llbracket \uu \rrbracket = 0, \quad 
  \llbracket \TT\nn \rrbracket = \ff, \quad 
  \nabla_{\gamma} \cdot \uu = 0, \quad \xx \in \gamma,
\end{align}
where $\ff$ is the total membrane force and $\nn$ is the outward unit
normal of $\gamma$.

@@

On the multicomponet vesicle $\gamma$ the velocity satisfies the no-slip boundary condition
$\frac{d\xx}{dt} = \uu(\xx)$, where $\xx(s,t)$ is the arclength
parameterization of $\gamma$. Along the solid wall $\Gamma$, we impose a
Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
Hagen–Poiseuille flow at the inlet and outlet (where $y\in[-W,W]$),
\begin{align}
  \UU(\xx) = U \left(1 - \left(\frac{y}{W}\right)^2 \right), 
    \quad \xx = (x,y) \in \Gamma,
\end{align}
and $\UU$ is zero along the top and bottom of the channel.
\todo[inline]{Need to define capillary number and diffusion time scale.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constitutive equations}
Using the same model as~\citet{liu-mar-li-vee-low2017}
and~\citet{soh-tse-li-voi-low2010}, the membrane forces depend on the
Helfrich energy, line tension, and phase energy. The phase and bending
energies are coupled through the bending modulus. In particular, the
individual energies are
\begin{align}
  E_b &= \frac{1}{2}\int_{\gamma} b(u) \kappa^2 \, ds, \quad
  E_t = \int_{\gamma} \sigma \, ds, \\
  E_p &= \frac{a}{\epsilon}\int_{\gamma}\left(
  f(u) +\frac{\epsilon^2}{2}|\nabla_\gamma u|^2\right) \, ds,
  \label{eqn:PhaseEnergy}
\end{align}
where $u$ is the dimensionless lipid concentration, $b(u)$ is the
lipid-dependent bending modulus, $\sigma$ is the vesicle's tension, and
$f(u) = \frac{1}{4}u^2(1-u)^2$ is the double-well potential with local
minimums at $u=0$ and $u=1$. Here, $\kappa$ is the membrane curvature,
$\ss$ is the tangent vector, and $s$ is the arclength. We have adopted
the same setup as~\citet{soh-tse-li-voi-low2010} where $\epsilon \ll 1$
is a dimensionless parameter that controls the size of the transition
region of $u$, and $a$ is the dimensional line tension scaled by
$b_{\max}/L$. Both $\epsilon$ and $a$ are kept constant in all
simulations. The resulting membrane forces are
\begin{align}
  \ff_b &= -(b(u)\kappa \nn)_{ss} -\frac{3}{2}
    \left(b(u) \kappa^2 \ss\right)_s, \\
  \ff_t &= (\sigma \ss)_s, \\
  \ff_p &= \left(\frac{a}{\epsilon}\left(f(u) -
     \frac{\epsilon^2}{2} u_s^2\right) \ss \right)_s.
\end{align}

\begin{figure}[H]
  \centering
%  \input{figures/concModels.tikz} \\
  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/concModels.pdf}
  \\
  \subfigimg[width=0.9\linewidth, clip ]{(b)}{figures/oldbending.pdf}
  \caption{\label{fig:concModels} \small (a) The linear bending model in
  red (equation~\eqref{eqn:linearBending}) and the new hyperbolic
  bending model in blue (equation~\eqref{eqn:tanhBending}). Note that
  the new bending model satisfies $b \in (\beta,1)$ even if $u \notin
  [0,1]$. (b) A multicomponent vesicle entering a closely-fitting
  channel using the linear model~\eqref{eqn:linearBending}. The vesicle
  bending modulus becomes negative, and this introduces an instability
  that first appears near the point with the largest negative curvature.
  }
\end{figure}

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard equation that results in the lipids phase separating while conserving their total mass. To model the variable bending, \citet{soh-tse-li-voi-low2010} propose parameterizing the bending modulus as
\begin{align}
    b(u) = (1-u) + \beta u.
    \label{eqn:linearBending}
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic when $u > 1$ since this results in $b(u) <
0$ if $u > (1 - \beta)^{-1}$, and such values of $u$ are possible when
$\beta \ll 1$, $Ca \gg 1$, or the vesicle is confined to a narrow
region.  Therefore, in this work we parameterize the bending modulus as
\begin{align}
    b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} \right)\right) + 
           \frac{\beta + 1}{2}.
    \label{eqn:tanhBending}
\end{align}
This maps the local minimums of the
double-well potential close to $\beta$ and $1$, but more
importantly, b(u) remains bounded in $(\beta,1)$ even when $u
\notin [0,1]$ (Figure~\ref{fig:concModels}(a)). To demonstrate the
necessity of this new bending model, we consider a multicomponent
vesicle in strong confinement with both bending
models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
maximum value of $u \approx 1.002$ which results in a  minimum bending
stiffness of $b(u) \approx \beta$. However, if we use the linear bending
model~\eqref{eqn:linearBending}, the lipid concentration achieves a
maximum value of $u \approx 1.52$ which results in an unphysical
negative bending stiffness of $b(u) \approx -0.5$. The corresponding
vesicle shape is in Figure~\ref{fig:concModels}(b), and the instability
caused by the negative bending stiffness is near the region with
negative curvature.
%\begin{figure}[htp]
%  \centering
%%    \begin{tabular}{@{}p{0.49\linewidth}@{\qquad}p{0.49\linewidth}@{}}
%  \subfigimg[width=0.48\linewidth, clip ]{(a)}{figures/newbending.pdf}
%%    \end{tabular}
%\caption{\label{fig:bendingModels} \small A multicomponent vesicle
%  entering a closely-fitting channel using (a) the new bending
%  model~\eqref{eqn:tanhBending}; (b) the linear
%  model~\eqref{eqn:linearBending}. With the linear model, the vesicle
%  bending modulus becomes negative, and this introduces an instability
%  that first appears near the point with the largest negative curvature.
%  The two plots are not at the same time step.}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:NumericalMethods}Numerical Methods}
The velocity field $\uu$ is written as a combination of a single-layer potential and a double-layer potential
\begin{align}
    \label{eqn:LPrep}
    \uu(\xx) = S[\ff](\xx) + D[\eeta](\xx),
\end{align}
where
\begin{align}
    S[\ff](\xx) &= \frac{1}{4\pi\mu} \int_{\gamma} \left(-\log \rho \mathds{I} + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) \, ds_\yy, \\
%
    D[\eeta](\xx) &= \frac{1}{\pi} \int_{\Gamma} \frac{\rr \cdot \nn}{\rho^2}
        \frac{\rr \otimes \rr}{\rho^2} \eeta(\yy) \, ds_\yy,
\end{align}
$\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times 2$ identity matrix. To avoid tangling of the vesicle membrane, it is parameterized in terms of the $\theta$-$L$ variables~\cite{hou-low-she1994}, where $L$ is the fixed vesicle length and $\theta$ is the opening angle of the tangent vector $\ss$. This requires decomposing the velocity field on $\gamma$ into its normal direction $V$ and tangential direction $T$. Then, the no-slip boundary condition for the vesicle velocity is
\begin{align}
    \frac{d\xx}{dt} = V \nn + T \ss + D[\eeta](\xx), \quad \xx \in \gamma.
\end{align}
The boundary condition on $\Gamma$ is imposed by requiring that $\eeta$ satisfies
\begin{align}
    \UU(\xx) = -\frac{1}{2}\eeta(\xx) + S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma.
    \label{eqn:DLP_BIE}
\end{align}
After discretizing the geometry at collocation points, the single-layer potential is approximated with quadrature for weakly-singular integrands, and the double-layer potential is approximated with the spectrally accurate trapezoid rule. All arclength derivatives are computed with spectral accuracy using Fourier methods. Time stepping is performed with second-order Adams-Bashforth. The resulting linear system is solved with GMRES.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation}
Since we use a new bending model, we first validate that it reproduces
the tank treading and phase treading dynamics reported in the
literature. Figure~\ref{fig:treading} shows a tank treading (top) and a
phase treading (bottom) multicomponent vesicle in an unconfined shear
flow. These simulations align with the results reported
by~\citet{liu-mar-li-vee-low2017} (cf.~Figures 3 and 4).
\begin{figure}[H]
  \centering
  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
  \caption{\label{fig:treading} \small A multicomponent (a)
  tank-treading and (b) phase-treading vesicle using the new bending
  model~\eqref{eqn:tanhBending}. These simulations agree with the
  results presented by~\citet{liu-mar-li-vee-low2017}.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle under strong confinement}

The lubrication layer between a vesicle and the solid wall plays a critical role on the vesicle's dynamics. Therefore, we report the size of the lubrication layers both above and below the vesicle in Section~\ref{sec:results}. We first justify the use of the term `lubrication layer' by verifying that the flow velocity is parabolic between the vesicle and the solid wall. Figure~\ref{fig:quadraticProof} illustrates the horizontal velocity (solid line) and the corresponding best fit quadratic (dashed line) in the co-moving frame, and the profiles agree.

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{figures/lubricationLayer_quadratic.pdf}  
    \caption{The co-moving velocity profile in the top and bottom lubrication layers. The red curve is the velocity profile, the dashed black line is the best quadratic fit.}
    \label{fig:quadraticProof}
\end{figure}

To define the size of the top lubrication layer (the size of the bottom
lubrication layer is defined similarly), we let
$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between the vesicle
and the top half of the confining geometry.
%\begin{align}
%    d(\xx,\Gamma_\mathrm{top}) = \inf_{\yy \in \Gamma_\mathrm{top}} \|\xx-\yy\|,
%\end{align}
%where $\Gamma_{\mathrm{top}}$ is the top portion of $\Gamma$.
We then find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with
the condition that $d(\xx,\Gamma_\mathrm{top}) < \beta$, where $\beta$
is a parameter. If no such local minimums exist, then the vesicle is too
far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
are two or more local minimums, the left-most, $\xx_L$, and right-most,
$\xx_R$, local minimums form the start and end of the lubrication layer.
If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the
points on $\gamma$ to the left and right of this local minimum with the
condition that $d(\xx_L,\Gamma_\mathrm{top}) =
d(\xx_R,\Gamma_\mathrm{top}) = \beta$. Then, the segment
$\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
\gamma$ between $\xx_L$ and $\xx_R$ with the condition that
$d(\xx,\Gamma_\mathrm{top}) < \beta$. Finally, the lubrication layer
width is
\begin{align}
    w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
\end{align}
The width of the bottom lubrication layer, $w_\mathrm{bot}$ is calculated replacing $\Gamma_\mathrm{top}$ with $\Gamma_\mathrm{bot}$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:Formulation}Formulation}
%\todo[inline]{Changes to be made to Figure~\ref{fig:schematic}.}
%\begin{itemize}
%  \item Remove labels $\Gamma$, $\Omega$, $\gamma$
%  \item Line on vesicle is too thick and change color scheme to same as
%    Fig 2
%  \item Change to a confined geometry that we use (stenosis)
%  \item Show a couple of vesicle shapes and the parabolic profile at
%    the inlet, outlet, and in the middle
%\end{itemize}
\begin{figure}[H]
  \centering
%  \includegraphics[trim = 0.3cm 0cm 1cm 0cm, clip=true,width=0.9\columnwidth]{figures/schematic.pdf}
  \includegraphics[width=0.9\columnwidth]{figures/schematic.pdf}
  \caption{\label{fig:schematic}\small A single multicomponent vesicle
  suspended in a strongly-confined stenosis. The color is the
  dimensionless stiffness which varies from $b_{\min} = 0.1$ to
  $b_{\max} = 1$. The vesicle dynamics are determined by a combination
  of phase, bending, and tension energies, and an imposed flow (blue
  arrows).}
%  \caption{\label{fig:schematic}\small A single multicomponent vesicle
%  with boundary $\gamma$ suspended in a domain $\Omega$ with boundary
%  $\Gamma$. The dark red regions are the ``stiff'' regions corresponding
%  to the maximum bending stiffness $b_{\max}=1$. The dark blue regions
%  are the ``floppy'' regions corresponding to the minimum bending
%  stiffness $b_{\min}=0.1$ The vesicle dynamics are determined by a
%  combination of phase, bending, and tension energies, and an imposed
%  flow on $\Gamma$. }
\end{figure}
We consider a single multicomponent vesicle $\omega$ with boundary
$\gamma$ suspended in a confined geometry $\Omega \subset \RR ^2$ with
boundary $\Gamma$ (Figure~\ref{fig:schematic}). The fluid is assumed to
have zero Reynolds number and is therefore governed by the
incompressible Stokes equations
\begin{align}
    \nabla \cdot \TT = 0 \quad \text{and} \quad \nabla \cdot \uu = 0, 
        \quad \xx \in \Omega \backslash \gamma,
\end{align}
where $\TT = -p\mathbf{I} + \mu\left(\nabla \uu + \nabla \uu^T \right)$
is the hydrodynamic stress tensor, $\uu$ is the velocity, $p$ is the
pressure, and $\mu$ is the fluid viscosity. Across the vesicle membrane,
we require that the velocity is continuous and locally inextensible, and
the membrane and hydrodynamic forces balance
\begin{align}
  \llbracket \uu \rrbracket = 0, \quad 
  \nabla_{\gamma} \cdot \uu = 0, \quad \xx \in \gamma, \quad
  \llbracket \TT\nn \rrbracket = \ff, 
\end{align}
where $\ff$ is the total membrane force and $\nn$ is the outward unit
normal of $\gamma$. By parameterizing $\gamma$ as $\xx(s,t)$, where $s$
is arclength and $t$ is time, the no-slip boundary condition is
$\frac{d\xx}{dt} = \uu(\xx)$.  Along the solid wall $\Gamma$, we impose
a Dirichlet boundary condition $\uu(\xx) = \UU(\xx)$, where $\UU$ is a
Hagen–Poiseuille flow at the inlet and outlet (where $y\in[-W,W]$),
\begin{align}
  \UU(\xx) = U \left(1 - \left(\frac{y}{W}\right)^2 \right), 
    \quad \xx = (x,y) \in \Gamma,
\end{align}
and $\UU$ is zero along the top and bottom of the channel.

@@

\todo[inline]{Need to define capillary number and diffusion time scale.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constitutive equations}
Using the model first introduced by~\citet{liu-mar-li-vee-low2017}, and
then investigated further by~\citet{soh-tse-li-voi-low2010}, the
membrane forces depend on the Helfrich energy, line tension, and phase
energy. The phase and bending energies are coupled through the bending
modulus. In particular, the individual energies are
\begin{align}
  E_b &= \frac{1}{2}\int_{\gamma} b(u) \kappa^2 \, ds, \quad
  E_t = \int_{\gamma} \sigma \, ds, \\
  E_p &= \frac{a}{\epsilon}\int_{\gamma}\left(
  f(u) +\frac{\epsilon^2}{2}|\nabla_\gamma u|^2\right) \, ds,
  \label{eqn:PhaseEnergy}
\end{align}
where $u$ is the dimensionless lipid concentration, $b(u)$ is the
lipid-dependent bending modulus, $\sigma$ is the vesicle's tension, and
$f(u) = \frac{1}{4}u^2(1-u)^2$ is a double-well potential with local
minimums at $u=0$ and $u=1$. Here, $\kappa$ is the membrane curvature
and $\ss$ is the tangent vector. We adopt the same setup
as~\citet{soh-tse-li-voi-low2010} where $\epsilon \ll 1$ is a
dimensionless parameter that controls the size of the transition region
of $u$, and $a$ is the dimensional line tension scaled by $b_{\max}/L$.
Both $\epsilon$ and $a$ are kept constant in all simulations. The
resulting membrane forces are
\begin{align}
  \ff_b &= -(b(u)\kappa \nn)_{ss} -\frac{3}{2}
    \left(b(u) \kappa^2 \ss\right)_s, \\
  \ff_t &= (\sigma \ss)_s, \\
  \ff_p &= \left(\frac{a}{\epsilon}\left(f(u) -
     \frac{\epsilon^2}{2} u_s^2\right) \ss \right)_s.
\end{align}

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard
equation that results in the lipids phase separating while conserving
their total mass. To model the variable bending,
\citet{soh-tse-li-voi-low2010} parameterized the bending modulus as
\begin{align}
  \label{eqn:linearBending}
  b(u) = (1-u) + \beta u.
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic when $u > 1$ since this results in $b(u) <
0$ if $u > (1 - \beta)^{-1}$, and such values of $u$ are possible when
$\beta \ll 1$, $Ca \gg 1$, or the vesicle is confined to a narrow
region. This behavior is demonstrated in Figure~\ref{fig:concModels}(a).
The stiff-to-floppy ratio is $\beta = 10^{-1}$. Using the linear bending
model~\eqref{eqn:linearBending}, the lipid concentration achieves a
maximum value of $u \approx 1.52$ which results in an instability that
is formed by a corresponding unphysical negative bending stiffness of
$b(u) \approx -0.5$. To rectify this issue, we parameterize the bending
modulus as
\begin{align}
  b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} 
    \right)\right) + \frac{\beta + 1}{2}.
  \label{eqn:tanhBending}
\end{align}
This parameterization maps the local minimums of the double-well
potential close to $\beta$ and $1$, but more importantly, b(u) remains
bounded in $(\beta,1)$ even when $u \notin [0,1]$
(Figure~\ref{fig:concModels}(b)). This new bending model is validated in
Section~\ref{sec:validation}.
%To demonstrate the necessity of this new bending model, we consider a
%multicomponent vesicle in strong confinement with both bending
%models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
%stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
%model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
%maximum value of $u \approx 1.002$ which results in a minimum bending
%stiffness of $b(u) \approx \beta$. However, if we use the linear
%bending model~\eqref{eqn:linearBending}, the lipid concentration
%achieves a maximum value of $u \approx 1.52$ which results in an
%unphysical negative bending stiffness of $b(u) \approx -0.5$. The
%corresponding vesicle shape is in Figure~\ref{fig:concModels}(b), and
%the instability caused by the negative bending stiffness is near the
%region with negative curvature.

\begin{figure}[H]
  \centering
%  \input{figures/concModels.tikz} \\
  \subfigimg[width=0.9\linewidth, clip ]{(a)}{figures/oldbending.pdf} \\
  \subfigimg[width=0.9\linewidth, clip ]{(b)}{figures/concModels.pdf}
  \caption{\label{fig:concModels} \small (a) A multicomponent vesicle
  entering a closely-fitting channel using the linear
  model~\eqref{eqn:linearBending}. The vesicle bending modulus becomes
  negative, and this introduces an instability that first appears near
  the point with the largest negative curvature. (b) The linear bending
  model in red (equation~\eqref{eqn:linearBending}) and the new
  hyperbolic bending model in blue (equation~\eqref{eqn:tanhBending}).
  Note that the new bending model satisfies $b \in (\beta,1)$ even if $u
  \notin [0,1]$.}
\end{figure}

%\begin{figure}[htp]
%  \centering
%%    \begin{tabular}{@{}p{0.49\linewidth}@{\qquad}p{0.49\linewidth}@{}}
%  \subfigimg[width=0.48\linewidth, clip ]{(a)}{figures/newbending.pdf}
%%    \end{tabular}
%\caption{\label{fig:bendingModels} \small A multicomponent vesicle
%  entering a closely-fitting channel using (a) the new bending
%  model~\eqref{eqn:tanhBending}; (b) the linear
%  model~\eqref{eqn:linearBending}. With the linear model, the vesicle
%  bending modulus becomes negative, and this introduces an instability
%  that first appears near the point with the largest negative curvature.
%  The two plots are not at the same time step.}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:NumericalMethods}Numerical Methods}
We use a high-order integral equation formulation to resolve the complex
vesicle shapes. The velocity field $\uu$ is written as a combination of
a single-layer potential and a double-layer potential
\begin{align}
  \label{eqn:LPrep}
  \uu(\xx) = S[\ff](\xx) + D[\eeta](\xx),
\end{align}
where
\begin{align}
  S[\ff](\xx) &= \frac{1}{4\pi\mu} \int_{\gamma} \left(
    -\log \rho \mathds{I} + \frac{\rr \otimes \rr}{\rho^2} \right)
    \ff(\yy) \, ds_\yy, \\
%
    D[\eeta](\xx) &= \frac{1}{\pi} \int_{\Gamma} 
      \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} \eeta(\yy) \, ds_\yy,
\end{align}
and $\rr = \xx - \yy$, $\rho = |\rr|$, and $\mathds{I}$ is the $2 \times
2$ identity matrix. To avoid tangling of the vesicle membrane, it is
parameterized in terms of the $\theta$-$L$
variables~\cite{hou-low-she1994}, where $L$ is the fixed vesicle length
and $\theta$ is the opening angle of the tangent vector $\ss$. This
requires decomposing the velocity field on $\gamma$ into a normal
velocity $V$ and tangential velocity $T$. Then, the no-slip boundary
condition for the vesicle velocity is
\begin{align}
  \frac{d\xx}{dt} = V \nn + T \ss + D[\eeta](\xx), \quad \xx \in \gamma.
\end{align}
The boundary condition on $\Gamma$ is imposed by requiring that $\eeta$
satisfies
\begin{align}
  \UU(\xx) = -\frac{1}{2}\eeta(\xx) + 
    S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma.
  \label{eqn:DLP_BIE}
\end{align}

The vesicle and solid walls are discretized at a set of collocation
points. The single-layer potential is then approximated using quadrature
for weakly-singular integrands, while the double-layer potential is
approximated using the spectrally accurate trapezoid rule. Arclength
derivatives are computed with spectral accuracy using Fourier methods.
Time stepping is carried out using the second-order Adams-Bashforth
method. Finally, the resulting linear system is solved using GMRES.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation}
\label{sec:validation}
We validate the new bending model~\eqref{eqn:tanhBending} by reproducing
the tank treading and phase treading dynamics reported in the
literature. Figure~\ref{fig:treading} shows a tank treading (top) and a
phase treading (bottom) multicomponent vesicle in an unconfined shear
flow. These simulations align with the results reported
by~\citet{liu-mar-li-vee-low2017} (cf.~Figures 3 and 4).
\begin{figure}[H]
  \todo[inline]{Change to new color scheme.}
  \centering
  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
  \caption{\label{fig:treading} \small A multicomponent (a)
  tank-treading and (b) phase-treading vesicle using the new bending
  model~\eqref{eqn:tanhBending}. These simulations agree with the
  results presented by~\citet{liu-mar-li-vee-low2017}.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle under strong confinement}

The lubrication layer between a vesicle and the solid wall plays a
critical role on the vesicle's dynamics. Therefore, throughout
Section~\ref{sec:results}, we will calculate the size and analyze the
flow structure inside the lubrication layers. 
%We first justify the use of the term `lubrication layer' by verifying
%that the flow velocity is parabolic between the vesicle and the solid
%wall. Figure~\ref{fig:quadraticProof} illustrates the horizontal
%velocity (solid line) and the corresponding best fit quadratic (dashed
%line) in the co-moving frame, and the profiles agree.
%
%\begin{figure}[H]
%    \centering
%    \includegraphics[width=\columnwidth]{figures/lubricationLayer_quadratic.pdf}  
%    \caption{The co-moving velocity profile in the top and bottom lubrication layers. The red curve is the velocity profile, the dashed black line is the best quadratic fit.}
%    \label{fig:quadraticProof}
%\end{figure}
To define the size of the top lubrication layer (the size of the bottom
lubrication layer is defined similarly), we let
$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between the vesicle
and the top half of the confining geometry.
%\begin{align}
%    d(\xx,\Gamma_\mathrm{top}) = \inf_{\yy \in \Gamma_\mathrm{top}} \|\xx-\yy\|,
%\end{align}
%where $\Gamma_{\mathrm{top}}$ is the top portion of $\Gamma$.
We then find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with
the condition that $d(\xx,\Gamma_\mathrm{top}) < \beta$, where $\beta$
is a parameter. If no such local minimums exist, then the vesicle is too
far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
are two or more local minimums, the left-most, $\xx_L$, and right-most,
$\xx_R$, local minimums form the start and end of the lubrication layer.
If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the
points on $\gamma$ to the left and right of this local minimum with the
condition that $d(\xx_L,\Gamma_\mathrm{top}) =
d(\xx_R,\Gamma_\mathrm{top}) = \beta$. Then, the segment
$\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
\gamma$ between $\xx_L$ and $\xx_R$ with the condition that
$d(\xx,\Gamma_\mathrm{top}) < \beta$. Finally, the lubrication layer
width is
\begin{align}
    w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
\end{align}
The width of the bottom lubrication layer, $w_\mathrm{bot}$ is calculated replacing $\Gamma_\mathrm{top}$ with $\Gamma_\mathrm{bot}$.
